\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-20 text/paper/paper.tex
Saturday, 20 January 2024 at 16:53:26

The experimental set-up consists of a Tandem accelerator, a beam line with electromagnets and a chamber with both the samples and the detectors.

Theoretically, the accelerator produces a beam of protons with a kinetic energy of up to 5 MeV, which is deviated by the steering electromagnet before hitting the sample. The electromagnet deflect particles with different angles according to their charge-to-mass ratio and, with that, allows us to remove any unwanted particles from the beam and only let the protons pass through.

The detectors used, which are silicon-based, detect charged particles through the ionisation they produce in the silicon.

In addition, the detectors are connected to a electronic system that amplifies the signal and sends it to a computer where the spectra can be seen.

The beam line is under a vacuum of around $10^{-7}$ mbar in order to avoid the protons colliding with other particles and losing energy. They reach the sample with the specified kinetic energy and cause a nuclear reaction whose products are the charged particles detected. We aim to analyse the energy spectrum of these particles.

@@

$E_{\alpha_{0_1}}$ and $E_{\alpha_{0_2}}$ are the energies of both alpha particles considering that they are in the fundamental state. In this case, the only other option would be for the $\ce{^8Be}$ to be formed in an excited state and therefore give origin to alpha particles also in an excited state. There is not enough energy for this to happen since the difference between the ground state and the the first state in an helium nuclei is very big, around $INSERT$ MeV.
\paragraph{}
Also, we can see that the scattering angle of the second alpha particle is around $12 ^{\circ}$ meaning that it is different from the detector's angle and will not be detected. To sum up, if there is lithium in any sample that reacts with the incoming protons according to \ref{eq:reactionLi}, we expect to detect alpha particles that were emitted with $7.6298 \text{ MeV}$.

>>>>

The experimental set-up consists of a Tandem accelerator, a beam line with electromagnets and a chamber with both the samples and the detectors.
Theoretically, the accelerator produces a beam of protons with a kinetic energy of up to 5 MeV, which is deviated by the steering electromagnet before hitting the sample. 
The electromagnets deflect particles with different angles according to their charge-to-mass ratio and, with that, allows us to remove any unwanted particles from the beam and only let the protons pass through.
The detectors used are silicon-based and detect charged particles through the ionization they produce in the silicon.
In addition, the detectors are connected to an electronic system that amplifies the signal and sends it to a computer where the spectra can be seen.
The beam line is under a vacuum of around $10^{-7}$ mbar in order to avoid the protons colliding with other particles and losing energy. 
They reach the sample with the specified kinetic energy and cause a nuclear reaction whose products are the charged particles detected. 
We aim to analyze the energy spectrum of these particles.

@@

$E_{\alpha_{0_1}}$ and $E_{\alpha_{0_2}}$ are the energies of both alpha particles considering that they are in the fundamental state. 
In this case, the only other option would be for the $\ce{^8Be}$ to be formed in an excited state and therefore give origin to alpha particles also in an excited state. 
There is not enough energy for this to happen since the difference between the ground state and the first state in a helium nucleus is very big.
\paragraph{}
Also, we can see that the scattering angle of the second alpha particle is around $12 ^{\circ}$ meaning that it is different from the detector's angle and will not be detected. To sum up, if there is lithium in any sample that reacts with the incoming protons according to \ref{eq:reactionLi}, we expect to detect alpha particles that were emitted with $7.6298 \text{ MeV}$.
